\subsection{Operational Requirements}

\subsubsection*{Usability}
\begin{itemize}
\item Navigation should be the first thing apart from the logo that the user spots in the system
\item It should be self-evident how to get to the desired part of a site (e.g., if user finds a show, it should be obvious how to get to a specific episode of that show)
\item Reloading the page should not be necessary for small tasks such as subscribing to a show
\item Signing up should not require more information from the user than is necessary, to encourage signing up and reduce amount of users who refrain from doing so
\item Sharing content from the site to social media should be simple and preferably done with a single click without bloating the front-end with unnecessary icons
\item The administrators should not need to re-learn everything. Since we are building this project on top of some existing code, the administrators should be able to do things the way they are used to.
\item The layout should be clean and minimalistic.
\end{itemize}

\subsubsection*{Availability}
\begin{itemize}
\item The application should have an uptime of at least 99\% (i.e. 24 hours/day, every day of the year) to be able to compete with other actors on the market, and to be able to provide a reliable API for mobile applications and potential third parties who may want to access data. 
\end{itemize}

\subsubsection*{Reliability}
\begin{itemize}
\item If a bug is discovered it should be patched as soon as possible. This should not take more than 48 hours from the time of notification.
\end{itemize}

\subsubsection*{Performance}
\begin{itemize}
\item The user should be able to quickly get data from the database (i.e. minimal latency).
\item The system should be able to handle 20.000 concurrent users with minimal delay.
\item When a user searches for something in the database, the delay before getting the results should never exceed 3 seconds.
\end{itemize}

\subsubsection*{Environment}
\begin{itemize}
\item To meet the demands of straight-forward further development of the system in the future and reduce time it takes to get into the code for new developers in the future using a well documented and popular language as the basis of the site is the only sensible decision - and therefore PHP will be used to develop the web system, as it is the most widely used open source language on the web. 
\item To be able to fulfull the performance goal of minimal latency and at the same time have a secure environment for the site to run in, a lightweight but secure web server with good performance should be used, i.e., nginx 
\item This project will also take advantage of a few open source libraries to accomplish the performance and availability goals.
\end{itemize}

\subsubsection*{Security}
\begin{itemize}
\item Personal information should be kept safe and encrypted in the database. No person should be able to access and read this information.
\item When a user pays the subscription fee, the data between the client and server should be transfered over a secure channel (i.e. SSL/TLS)
\item A users payment information (e.g. creditcard numbers etc.) should not be saved in the database.
\end{itemize}