\subsection{Goals and frameworks}
\subsubsection{Background}
FrostByte, a fictional company,  is a company specializing in informative web solutions for everything related to TV-shows.
The company has previously had a decent product which covered their basic needs, but has recently been met with increasing competition. Because of this, they’ve decided to further develop their product and give their existing and new users a completely new product with increased functionality which they hope will give them a competitive edge.

\subsubsection{Brief description of product}
The final product should present users with a grid of all TV-shows known to man. Users should be able to browse through TV-shows, view details about them, as well as details about every individual episode.
Users should also be able to create user accounts, to allow them to log in and access otherwise unavailable features. Such features may include e.g \textit{following} specific TV-shows, generating a calendar view of upcoming episode release dates for followed shows, and mobile push notifications.

It goes without saying that users should be able to search for shows, actors and/or episodes, and filter shows using a variety of different categories such as channel it was originally broadcast on, who acts in it, or what rating it has been given on international sites such as IMDb.

It should be possible to assign users roles, such as Administrator, Moderator, Grand Suncrusher or Newly Registered through the administrator interface. An administrator should also be able to \textit{force} an update of the contents in the database (something which should otherwise be done in regular intervals automagically). 

The design needs to be responsive, as to adapt well for hand held devices.

\subsubsection{Goals}

\paragraph{Expected results}~\\
It’s expected that the finished product should be able to:\\
       -    register new users\\
       -    allow users to stay up-to-date with new and old TV-shows\\
       -    suggest new TV-shows based on the users preferences\\
       -    distribute e-mail to all users when there are significant news (news letters)\\
       -    export TV-schedule to an existing calendar (iOS, Android, WP8)\\
       -    offer advertising space to other companies\\
       -    allow users to pay for additional functionality\\
       -    the platform should also be easily managed and maintained. 

\paragraph{Expected impact}~\\
By developing this system, the company expects the following effects:\\
      -    Increased publicity\\
      -    By utilizing new technology and functionality, become leading within their niched market\\
      -    30\% increased profit the first year\\
      -    40\% more visitors

\subsubsection{Frameworks}
The project is executed and delivered within the provided framework.

\paragraph{Legal framework}

The finished system may not violate the Norwegian Personal Data Act §§8-17

\paragraph{Technological frameworks}~\\
The system should have gone through a thorough security audit before being handed over, to ensure the safety of users’ information.

\paragraph{Budget and time frame}~\\
FrostByte has stated they want the system up and running by 15. dec. 2014. Furthermore, the project has a budget of 3.5 million NOK.
